### 2022-11-29 writeups/Observations.tex
add tf-idf rules-based model

Three machine learning models were used: SVMs, Decision Trees, and Naïve Bayes classifiers. Each of those models was used for Boolean and type classification and with three seperate text representations (Bag-of-Words, raw frequency, and TF-IDF), making a total of 12 models. For the sake of evaluation, the rules-based model was retrained on only the training data, then tested on the test data. Models labeled RB are rules-based. The scores represent the proportion of the test dataset that the model correctly predicted, 1 means perfect predictions, 0 means entirely incorrect predictions.
\begin{center}
Table 3: Machine learning model evaluations and comparisons to rules-based model
\begin{tabular}{ |c|c|c|c| }
\hline {\bf Model type} & {\bf Text representation} & {\bf Boolean score} & {\bf Type score} \\
\hline Decision Tree & BoW & 0.653 &  0.513\\
\hline Decision Tree & Frequency & 0.695  &  0.692\\
\hline Decision Tree & TF-IDF & 0.703 & 0.487\\
\hline SVM & BoW & 0.703 & 0.692\\
\hline SVM & Frequency & 0.703 & 0.564\\
\hline SVM & TF-IDF & 0.678 & 0.462\\
\hline Naïve Bayes & BoW & 0.669 & 0.769\\
\hline Naïve Bayes & Frequency & 0.602 & 0.487\\
\hline Naïve Bayes & TF-IDF & 0.602 & 0.462\\
\hline Cosine Similarity (RB) & Frequency & 0.602 & 0.462\\
\hline Vector Distance (RB) & Frequency & 0.602 & 0.462\\
\hline
\end{tabular}
\end{center}
\end{document}

>>>>

Three machine learning models were used: SVMs, Decision Trees, and Naïve Bayes classifiers. Each of those models was used for Boolean and type classification and with three seperate text representations (Bag-of-Words, raw frequency, and TF-IDF), making a total of 18 models. For the sake of evaluation, the rules-based model was retrained on only the training data, then tested on the test data. Models labeled RB are rules-based. The scores represent the proportion of the test dataset that the model correctly predicted, 1 means perfect predictions, 0 means entirely incorrect predictions.
\begin{center}
Table 3: Machine learning model evaluations and comparisons to rules-based model
\begin{tabular}{ |c|c|c|c| }
\hline {\bf Model type} & {\bf Text representation} & {\bf Boolean score} & {\bf Type score} \\
\hline Decision Tree & BoW & 0.653 &  0.513\\
\hline Decision Tree & Frequency & 0.695  &  0.692\\
\hline Decision Tree & TF-IDF & 0.703 & 0.487\\
\hline SVM & BoW & 0.703 & 0.692\\
\hline SVM & Frequency & 0.703 & 0.564\\
\hline SVM & TF-IDF & 0.678 & 0.462\\
\hline Naïve Bayes & BoW & 0.669 & 0.769\\
\hline Naïve Bayes & Frequency & 0.602 & 0.487\\
\hline Naïve Bayes & TF-IDF & 0.602 & 0.462\\
\hline Cosine Similarity (RB) & Frequency & 0.602 & 0.462\\
\hline Vector Distance (RB) & Frequency & 0.602 & 0.462\\
\hline Vector Distance (RB) & TF-IDF & 0.602 & 0.462\\
\hline
\end{tabular}
\end{center}
\end{document}
